\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{varwidth}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright
\usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{scrextend}
\usepackage{enumitem}
\usepackage{tabularx}

\hypersetup{
    colorlinks=false,
}
\urlstyle{same}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
    \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
        {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [4] {
    \textbf{#1} \hfill {#3} \\
    \textit{#2} \hfill {#4} \\
    \vspace{0mm}
}

\newcommand{\education} [5] {
    \textbf{#1} \hfill {#4} \\ {#5} \\ \vspace{1mm}
    \begin{tabularx}{\textwidth}{@{}p{3cm} X@{}}
    \textbf{Degree:} & {#2} \\
    \textbf{Qualification:} & {#3} \\
    \end{tabularx}
    \vspace{2mm}
}

\newcommand{\project} [4] {
    \textbf{#1} \hfill {#4} \\ \vspace{1mm}
    \begin{addmargin}[0em]{1em}
    \begin{tabularx}{\textwidth}{@{}p{3cm} X@{}}
    \textbf{Tools:} & {#2} \\
    \textbf{Description:} & {#3} \\
    \end{tabularx}
    \end{addmargin}
    \vspace{2mm}
}

\def\email{nekto.denis.v@gmail.com}
\def\phone{555-55-55}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \vspace*{-40pt}


%==== Profile ====%
    \vspace*{-10pt}
    \begin{center}
        \Huge \scshape {Denis O. Vodopianov} \\ \vspace{1mm}
    \end{center}

    \begin{center}
        Berlin, Germany $\cdot$
        \href{mailto:\email}{\email} $\cdot$
%        \href{tel:\phone}{\phone} $\cdot$
        \url{https://github.com/grambbledook}\\
    \end{center}

    \header{About}
    \begin{raggedright}

        Software engineer with a decade of experience specializing in distributed systems, with a focus on scalability, reliability, and performance.
        I have experience moving from monoliths to microservices to scale a business and back to microliths
        to optimize cost and performance. \break

        I enjoy solving various system problems as well as low-level algorithmic challenges.
        My key strengths include analytical thinking, empathy, a strong bias for action, ownership, and a focus on customer needs. \\
    \end{raggedright}
    \vspace{2mm}

    \header{Skills}
    \begin{tabularx}{\textwidth}{p{5cm} X}
        Programming Languages: & Kotlin, Java, Scala, Python, Go, Typescript                                                                     \\
        Web Frameworks:        & Spring Boot, Vert.x, Netty, Play, Express.js                                                                    \\
        DevOps:                & Docker, Kubernetes, Terraform, Ansible, Jenkins, Gitlab CI/CD, Argo CD, Datadog, ELK stack, Grafana, Prometheus \\
        Databases:             & Postgres, Mongo, DynamoDB, Cassandra, Redis                                                                     \\
        Networking:            & TCP/IP, HTTPS, WebSockets                                                                                       \\
        Big Data:              & Hadoop, Hive, Pig, Hbase, Clickhouse, Storm, Spark, Airflow                                                     \\
    \end{tabularx}
    \vspace{2mm}


%==== Experience ====%
    \header{Work Experience}
    \vspace{1mm}

    \employer{Trade Republic Bank}{Senior Software Engineer}{October 2023 - April 2024}{Berlin, Germany}
    \begin{itemize}[itemsep=-1mm]
        \item Was in charge of user accounts and balances.
        Made system consistent, fast, and highly available.
        \item Resolved integration issues, and delivered a system required for Cards product launch.
        \item Identified and fixed slow spots, reduced response latency from 20 to 5 ms.
        \item Built a reconciliation system that processes 150M transactions daily to keep banking data consistent.
    \end{itemize}

    \employer{Picsart}{Senior Software Engineer II (Lead Engineer) - Data Platform}{January 2022 - March 2023}{Berlin, Germany}
    \begin{itemize}[itemsep=-1mm]
        \item Owned user tracking component in analytics platform handling billions of events per day, peak 200k eps.
        \item Implemented edge component with auth and back-pressure mechanisms for analytics platform using Envoy-based API gateway.
        \item Optimised event ingestion, reduced fleet by 40\% and freed up resources.
        \item Reduced change failure rates by adding quality checks, tests, feature-flags and alerts.
        \item 10x faster deployments by switching to trunk-based development, reusable CI/CD components.
        \item Mentored engineers, improved ownership, quality, reduced debt.
    \end{itemize}

    \employer{N26 GmbH}{Senior Software Engineer - Identity, Acting Tech Lead}{March 2020 - January 2022}{Berlin, Germany}
    \begin{itemize}[itemsep=-1mm]
        \item Full ownership of identity platform with focus on security, scalability, reliability and compliance.
        \item Implemented strong customer authentication for PSD2 compliance.
        \item Worked with product and ML on R\&D projects, creating a roadmap to improve security of the platform.
        \item Automated access recovery for non-German customers, improving UX and cutting costs.
        \item Designed and implemented various authentication mechanisms for n26 products.
        \item Participated in on-call and incident response, addressing issues and minimizing downtime.
    \end{itemize}

    \employer{Freelance, Contractor}{Lead Software Engineer at Plutus.ai}{November 2018 - February 2020}{Saint–Petersburg, Russia}
    \begin{itemize}[itemsep=-1mm]
        \item Led a team of five engineers to deliver casual crypto portfolio with gamification and social elements.
        \item Identified and resolved scalability issues to meet the demands of a growing client base.
        \item Switched system from batched to NRT data processing, enhanced gamification mechanics.
        \item Built framework for fast integration with exchanges and news outlets.
    \end{itemize}

%    \employer{Nexign Systems}{Lead Software Engineer}{August 2017 - September 2018}{Saint–Petersburg, Russia}
%    \begin{itemize}[itemsep=-1mm]
%        \item Led a team of seven engineers, delivered software updates on time.
%        \item Refreshed legacy PRM system for cloud, made it more efficient.
%        \item Designed load testing framework, optimised system performance.
%    \end{itemize}
%
%    \employer{Contractor, multiple clients}{Senior Software/Data Engineer}{June 2014 - August 2017}{Saint–Petersburg, Russia}
%    \begin{itemize}[itemsep=-1mm]
%        \item Made system for testing and rolling out statistics and ML models
%        \item  Implemented integrations with various third party systems to build the state-of-art fraud detection component
%    \end{itemize}
%
%    \employer{Oracle}{Software Developer in Test, Java JDK}{November 2012 - June 2014}{Saint-Petersburg, Russia}
%    \begin{itemize}[itemsep=-1mm]
%        \item Designing comprehensive tests for multiple features including potential and real security vulnerabilities.
%        \item Improved stability and performance of the testing framework, enhancing overall productivity and reliability
%        in the testing process.
%        \item Led Nightly build report analysis, implemented a number of system enhancements, that helped to automate report
%        generation, resulting in improved efficiency and accuracy in bug triaging and resolution
%    \end{itemize}


%==== Education ====%
    \header{Education}

    \education{ITMO University}
    {Master’s degree in Optical Electronic Devices and Systems with specialisation in Optical-Electronic Devices and Systems for Video Information Processing}
    {Engineer}
    {Saint–Petersburg, Russia}
    {September 2004 - February 2010}


%==== Notable Projects ====%
    \header{Projects}
    \project{\textbf Indoor cycling HUD}
    {C++, Bluetooth Low Energy, QT, sqlite, CMake, vcpkg}
    {An overlay app that aggregates data coming from BLE devices and renders workout statistics on the heads up display}
    {https://github.com/grambbledook/indoor-cycling-hud}
%
%    \project{Identity platform for a challenger bank}
%    {Kotlin, Java, AWS, Terraform, Kubernetes, Redis, Kafka, Go.}
%    {Highly scalable and resilient system capable of handling millions of authentication and authorization requests per day}
%    {2020-2022}
%
%    \project{ML deployment platform}
%    {Python, Scala, Java, Airflow, Hive, Spark, Hbase, Kafka, Parquet, Avro and a dozen of glue tools}
%    {Platform for statistical and ML models production deployment with support of AB testing and model versioning}
%    {2015-2017}

\end{document}